The intended audience for the \texttt{\getsoftwarename{}} Application (\texttt{\getsoftwarename{}} App) is researchers and practitioners
interested in quantification of the seismic performance of buildings.\\

This is an open-source, research application. The source code at
the \href{https://github.com/NHERI-SimCenter/PBE}{\texttt{\getsoftwarename{}}
Github page} provides an application that can be used to assess the performance of a building in an earthquake scenario. The application focuses on quantifying building performance through decision variables. Given that the properties of the buildings and the earthquake events are not known exactly, and that the simulation software and the user make simplifying assumptions in when modeling the seismic event and the structural response, the estimated response of the structure already exhibits significant variability. Structural response and its uncertainty can be estimated using our \href{https://simcenter.designsafe-ci.org/research-tools/ee-uq-application/}{\texttt{EE-UQ} Application}. The \texttt{\getsoftwarename{}} App builds on the \texttt{EE-UQ} App and uses its response estimates to assess the damage to building components and the consequences of such damage.\\

The user can characterize the structural model, the damage and loss model, and the seismic hazard model in this application. All models are interconnected by an uncertainty quantification framework that allows the user to define a stochastic model for the problem. Given that stochastic model, the application first performs nonlinear response-history simulations to obtain the Engineering Demand Parameters (EDPs) that describe structural response. Then, those EDPs are used to assess the Damage Measures (DMs) and Decision Variables (DVs) that characterize building performance.\\

Depending on the type of structural system, the fidelity of the structural model, and the number of EDP samples, the response-history simulations can be computationally prohibitively expensive. To overcome this impediment, the user can choose to perform the response simulations on the Stampede2 supercomputer. Stampede2 is located at the Texas Advanced Computing Center (TACC) and made available to the user through NHERI DesignSafe-CI, the cyberinfrastructure provider for the distributed, NSF-funded, Natural Hazards Engineering Research Infrastructure (NHERI) facility.\\

The computations are performed, as will be discussed in \Cref{chap:theory}, with a Workflow Application. A Workflow Application is a sequence of tools linked together. The \texttt{\getsoftwarename{}} backend runs those tools, taking the outputs from some programs and providing them as inputs to others. Researchers can extend the Workflow Application to use their own tools in the backend computations. This ensures that researchers are not limited to using the default applications we provide and will be enthused to provide their own applications for others to use.\\

This is Version \getsoftwareversion{} of the tool. Users are
encouraged to comment on what additional features and capabilities
they would like to see in this application. These requests and
feedback can be submitted through an anonymous \insertsurveylink{user
survey}; we greatly appreciate any input you have. If there are
features you want, chances are many of your colleagues also would
benefit from them. Users are encouraged to review
\Cref{chap:requirements} to see what features are planned for future releases.
